---
title: "HW2"
author: "Mauro Gonzalez"
date: "2025-09-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(faraway)

```

**Q1A.** *What are the advantages and disadvantages of a very flexible (versus a less flexible) approach for regression or classification?*

Flexible methods can more realistic, as there can be a variety of factors that influence outcomes, as opposed to only one or two. However, such flexible models can be overly-complex and less-readiable. There is also the potential of "overfitting" a model, in which the model reacts to random noise and various minutia, decreasing its use.

**Q1B.** *Under what circumstances might a more flexible approach be preferred to a less flexible approach? When might a less flexible approach be preferred?*

Given the more exact nature of flexible approaches, they may be useful in more 'academic' contexts - where extrmely accurate forecasting is required. Meanwhile, less flexible approaches may be useful to figure out if general inferences hold up, see the direction of trends, and so on.

**Q2A**

```{r}
lm(wage ~ educ+exper, data = uswages)

lm(wage~educ, data=uswages)
```

Holding experience constant, each additional year of education is associated with an increased \$51.175 in wages

**Q2B**

```{r}
uswages$loggedwage <- log(uswages$wage)
lm(loggedwage ~ educ+exper, data=uswages)
```

Hold experience constant, each additional year of education is associated with a 9% increase in wages

Q2C: The model in 2A is more natural, due to the fact that it is easier to visualize specific dollar amounts as opposed to a percentage/logged increase.
